Supplement

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
table MLM exploratory

>>>>

## Exploratory analysis: Association between SVs and self-control and NFC

``` {r TabExp, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  Exp_M3_table,
  caption = "Exploratory analysis: Results of MLM predicting SVs of ER strategies with level 2 predictors self-control and NFC.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```
